---
title: "convert_pitch_object_10ms"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# CONTRASTIVE stress files WOMEN only
This R script processes a list of WOMEN'S .wav audio files to extract pitch data using Praat. It takes audio files from a specified input directory, converts each file into a Praat pitch object, and saves the output in a specified output directory. The script utilizes the PraatR, dplyr, and purrr libraries to automate the batch processing of files, ensuring that each .wav file is transformed into a corresponding .Pitch file for further acoustic analysis.

```{r}
# Load necessary libraries
library(PraatR)
library(dplyr)
library(purrr)

# Define input and output directories
input_dir <- "D:/IntroDataScienceProject/crema-d-mirror/MFA/Men"
output_dir <- "D:/IntroDataScienceProject/crema-d-mirror/MenPitchFiles"

# Get list of .wav files from the input directory
file_list <- list.files(path = input_dir, pattern = "\\.wav$", full.names = TRUE)

# Extract file names  
file_names <- basename(file_list)
  
# Function to convert wav file to pitch object
to_pitch_object <- function(fname, input_dir, output_dir) {
  input_file <- file.path(input_dir, fname)
  output_file <- file.path(output_dir, sub(".wav$", ".Pitch", fname))
  
  # Praat command to convert wav to pitch object
  #80 to 450 is for females
  #30 to 400 is for males
  praat("To Pitch...", arguments = list(0.025, 30, 400), 
        input = input_file, 
        output = output_file, 
        overwrite = TRUE)
}

# Apply the function to all files
map(file_names, to_pitch_object, input_dir = input_dir, output_dir = output_dir)


# Update the 'input_dir' and 'output_dir' variables to point to the desired directories.

```

